Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 paper/paper.Rmd
Start fixing up code snippets

```{r, results='asis'}
project_plan_raw <- read_csv("data/planning_and_outcomes.csv")

@@

% latex table generated in R 3.3.0 by xtable 1.8-2 package
% Fri Jun 24 12:02:11 2016
\begin{table}[ht]
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
  \hline
@storm2015 & 3 & No & No & No &  48 &  61 \\ 
@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
@liverence2015 & 1 & No & Some & No &  18 &  \\ 
@wang2015 & 2 & No & No & No & 219 & 397 \\ 
@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
@xu2015 & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{Summary of attempted replications} 
\label{tab:summary}
\end{table}

@@

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}. Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk. All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

Of the `{r} nrow(ppt)` studies included in the final sample, `{r} round(mean(ppt$open_materials == "Yes" | ppt$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. For `{r} sum(!is.na(authors_contact))` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors). Responses were received in all but one case, usually within a matter of days.

@@

```{r}
project_plan %>% 
  group_by(fidelity) %>%
  summarise(replicated = mean(replicated_TA))
```

>>>>

```{r, results='asis'}
project_plan_raw <- read.csv("data/planning_and_outcomes.csv")

@@

<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
 Fri Jun 24 12:02:11 2016 -->
\begin{table}[ht]
\centering
\begin{tabular}{lllllrr}
  \hline
Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
  \hline
@storm2015 & 3 & No & No & No &  48 &  61 \\ 
@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
@liverence2015 & 1 & No & Some & No &  18 &  \\ 
@wang2015 & 2 & No & No & No & 219 & 397 \\ 
@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
@xu2015 & 1a & No & No & No &  12 &  27 \\ 
   \hline
\end{tabular}
\caption{Summary of attempted replications} 
\label{tab:summary}
\end{table}

@@

All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}. Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk. All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."

@@

Of the `r nrow(ppt)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors). Responses were received in all but one case, usually within a matter of days.

@@

```{r}
project_plan %>% 
  group_by(replication_fidelity_MCF) %>%
  summarise(replicated = mean(replicated_TA))
```
